### 2020-03-26 defesa/article/definition.tex
dissertacao depositada

We define an instance of the one-facility MCE or MCER as $(\Pp, \Ww, \{(a,b)\})$ omitting the facility index in every notation. For example, a solution of MCER is denoted as $Q := (q, \theta)$.

>>>>

In some cases, it will be more convenient to work with the one-facility version of MCE or MCER. When that is the case, we use an adapted notation removing all the unnecessary indexes, sequences and sets used to specify multiple facilities. For example, a solution of the one-facility MCER is denoted by $Q:=(q,\theta)$.

### 2020-03-26 defesa/tex/chapter/definicoes.tex
wip
dissertacao depositada

A circle (or circumference) is a set of points in $\R^2$ that have the same Euclidean distance, also known as radius, to another point, also referred to as the center of the circle. A unit circle is a circle with radius equal to $1$.

@@

Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$, centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$. Suppose that this line intersects the ellipse at least at one point. Plugging the line's equation into \autoref{equation:pellipse}, it is possible to obtain the distance between the intersection points. The final expression is given by
\begin{equation*}\label{eq:dist_line_ellipse}
D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
\end{equation*}
with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$. It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$. From that, we can conclude that if $m$ is fixed, the line that has the most distant intersection points with an ellipse is the one that passes through the origin; and also, that $D(m, c)$ attains every value in the range $[0, D(m, 0)]$. 
Following that, we define a function $L:\R\mapsto\R_{>0}$ as

\begin{equation}\label{eq:function-l}
L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2},
\end{equation}
which describes the maximum distance between points of an ellipse-line intersection considering all lines with $m$ angular coefficient.

It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $m=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty\, 0]$, and attains every value in the interval $(4b^2, 4a^2]$. Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
In \autoref{fig:L-function-plot}, an example of function $L$ is shown with $(a, b) = (2, 1)$.

	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
	\includegraphics[scale=.4]{tex/figures/L-function-plot}
	\fautor
	\label{fig:L-function-plot}
\end{figure}

@@

An ellipse rotated by $\theta$ can be transformed into an axis-parallel, and origin-centered ellipse by applying two linear transformations: translation to make its center be at $(0, 0)$, and rotation to make its major axis parallel to the $x$-axis. Reversing these transformations produces the following equation for a non-axis-parallel ellipse
\begin{equation}\label{eq:rotated_ellipse}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}=1.
\end{equation}
The coverage region of that same ellipse is given by every point $(x, y)\in\R^2$ that satisfies the following equation
\begin{equation}\label{eq:rotated_ellipse_co}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1,
\end{equation}
which is the same as \autoref{eq:rotated_ellipse} with the equality sign $(=)$ replaced by $(\le)$.

>>>>

A circle (or circumference) is a set of points in $\R^2$ that have the same Euclidean distance, also known as radius, to another point, also referred to as the center of the circle. A unit circle is a circle with radius equal to one.

@@

Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$, centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$. Suppose that this line intersects the ellipse at least at one point. Plugging the line's equation into \autoref{equation:pellipse}, we get
\begin{align}
\frac{x^2}{a^2}+\frac{(mx + c)^2}{b^2} -1 &= 0 \nonumber\\
x^2\left(\frac{1}{a^2} + \frac{m^2}{b^2}\right) + \frac{2mxc}{b^2} + \frac{c^2}{b^2} - 1 &= 0\nonumber.
\end{align}
Let $(x_1, y_1)$, and $(x_2, y_2)$ be the ellipse-line intersection points. Then, we have that
\begin{align}
(x_1-x_2)^2 &= \frac{\frac{4m^2c^2}{b^4} - 4\left(\frac{1}{a^2} + \frac{m^2}{b^2}\right)\left(\frac{c^2}{b^2}-1\right)}{\left(\frac{1}{a^2} + \frac{m^2}{b^2}\right)^2}\nonumber\\
(x_1-x_2)^2 &= \frac{4m^2c^2a^4}{(b^2+a^2m^2)^2} - \frac{4(c^2-b^2)a^2}{b^2+a^2m^2}\nonumber\\
(x_1-x_2)^2 &= 4\frac{m^2c^2a^4 - (b^2+a^2m^2)(c^2-b^2)a^2}{(b^2+a^2m^2)^2}\nonumber\\
(x_1-x_2)^2 &= 4\frac{a^2b^2(a^2m^2 + b^2 -c^2)}{(b^2+a^2m^2)^2}\nonumber.
\end{align}
Then, as $(y_1-y_2)^2 = (mx_1 - mx_2)^2 = m^2(x_1-x_2)^2$, we get the final expression for the distance between two ellipse-line intersection points
\begin{equation*}
\sqrt{(x_1-x_2)^2+(y_1-y_2)^2}=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)}.
\end{equation*}

%\begin{figure}[H]
%	\centering

%	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
%	\includegraphics[scale=.4]{tex/figures/L-function-plot}
%	\fautor
%	\label{fig:L-function-plot}
%\end{figure}

@@

An ellipse rotated by $\theta$ can be transformed into an axis-parallel, and origin-centered ellipse by applying two linear transformations: translation to make its center be at $(0, 0)$, and rotation to make its major axis parallel to the $x$-axis. Reversing these transformations produces the following equation for a non-axis-parallel ellipse
\begin{equation}\label{eq:rotated_ellipse}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}-1=0.
\end{equation}
The coverage region of that same ellipse is given by every point $(x, y)\in\R^2$ that satisfies the following equation
\begin{equation}\label{eq:rotated_ellipse_co}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1,
\end{equation}
which is the same as \autoref{eq:rotated_ellipse} with the equality sign $(=)$ replaced by $(\le)$.

### 2020-03-26 defesa/tex/chapter/mcd2.tex
dissertacao depositada

Let $(\Pp, \Ww, \{||\cdot||\})$ be an instance of MCSCD with only one facility, and $(\Pp, \Ww, ||\cdot||)$ an instance of MWC.
If $q_1$ be a solution for the MCSCD's instance. Then, the disks with centers in $\Pp \cap E_1(q_1)$ have a non-empty intersection.
Also, suppose that $q$ is a solution of MWC. Then, the ellipse with shape parameters $(a, b)$ centered at $q$ covers the points, which are the centers of disks, such that $q \in D_j$.
Therefore, MCSCD and MWC for both problems are equivalent.

>>>>

Let $(\Pp, \Ww, ||\cdot||)$ be an instance of MCSCD with only one facility, and $(\Pp, \Ww, ||\cdot||)$ an instance of MWC.
If $q_1$ be a solution for the MCSCD's instance. Then, the disks with centers in $\Pp \cap E_1(q_1)$ have a non-empty intersection.
Also, suppose that $q$ is a solution of MWC. 
Then, the $D(q)$ covers the points, which are the centers of disks, such that $q \in D_j$.
Therefore, MCSCD and MWC for both problems are equivalent.
